Classless Java

### 2015-10-02 paper/sections/Formalization.tex
example code on method shadowing mechanism in Java
comments on shadow function
type checking of interfaces

\subsubsection{Method Typing}

\marco{I can not understand those rules, when is t-meth and t-meth body called? when is that you state that all methods in all interfaces must be ok?}
\[ 
\inferrule 
{ }
{T_0 \spc m(\overline{T} \spc \overline{x}); \text{ OK IN I} }
\quad \textsc{(T-Meth)}
\]

\[ 
\inferrule
{\overline{x}:\overline{T} \vdash e:S \\ S <: T_0}
{T_0 \spc m(\overline{T} \spc \overline{x}) \text{ \{ return } e;\} \text{ OK IN
    I} \\\\ \Gamma \vdash \textbf{this}:I }
\quad \textsc{(T-MethBody)}
\]

@@

@@

\subsection{Auxiliary Definitions}
\yanlin{todo: add more auxiliary functions}

\yanlin{todo: add interface context}

@@

>>>>

\subsubsection{Typechecking of Methods}

\marco{I can not understand those rules, when is t-meth and t-meth body called? when is that you state that all methods in all interfaces must be ok?}
\begin{comment}
\[ 
\inferrule 
{ }
{T_0 \spc m(\overline{T} \spc \overline{x}); \text{ OK IN I} }
\quad \textsc{(T-Meth)}
\]

\[ 
\inferrule
{\overline{x}:\overline{T} \vdash e:S \\ S <: T_0}
{T_0 \spc m(\overline{T} \spc \overline{x}) \text{ \{ return } e;\} \text{ OK IN
    I} \\\\ \Gamma \vdash \textbf{this}:I }
\quad \textsc{(T-MethBody)}
\]
\end{comment}

@@

\subsubsection{Typechecking of Interfaces}
\[ \inferrule
{\textbf{interface } I \textbf{ extends } \overline{J} \{ \overline{M} \} \\\\
 \forall J_i \in \overline{J}, J_i \text{ OK} \\\\
 \forall m \in \overline{M}, \textsf{mbody}(m,I) \neq ERROR \\\\
 \forall J_i \in \overline{J}, \forall m \text{ inside } J_i,
 \textsf{mbody}(m,I) \neq ERROR }
{I \text{ OK}}
\quad \textsc{(T-Intf)}
 \]

Interface $I$ type checks well, if:
\begin{itemize}
\item All its super-interfaces $\overline{J}$ OK.
\item All methods inside interface $I$ are OK.
\item All methods that $I$ is inheriting from super-interfaces are OK.      
\end{itemize}

@@

\subsection{Auxiliary Definitions}

@@

\yanlin{for \textbf{shadow} conflicted mh;, one missing case is when there are
  two conflicting default methods with same signature?? }

\yanlin{for \textbf{override}, what's the result if arguments for override
  doesn't match any given rule. For example, override(a static method, mh'). It
  would return UNDEFINED or generate ERROR??}
